Using demographic accounts to enhance official population statistics

### 2021-11-06 article.tex
deleted fig

Publishers of age-structured demographic data typically use some variant of the following scheme,
\begin{center}
\includegraphics[width=0.4\textwidth]{figures_accounts/fig_account_withage2.pdf}
\end{center}
Population stocks stocks and flows are all disaggregated by the same age groups, which, in the case above, are ages 0, 1, and 2+. (The account in question might apply to non-human animals, or use a unit of measurement that is longer than a year.) The final age group includes everone over a certain age. Births are disaggregated by the age of the mother, rather than the age of the child being born, which is always 0.

@@

To do for each age group, need to deaths into ones that occurred to cohort already in age group and cohort entering age group:
\begin{center}
\includegraphics[width=0.5\textwidth]{figures_accounts/fig_account_withage.pdf}
\end{center}

\begin{align}
    8 - (3 + 4) & = -2 + 3 - 1 & \text{Age 0 at $t+1$} \\   
    9 - 7 & = -(1 + 1) + (4 + 2) - (0 + 2) & \text{(Age 1 at $t+1$)} \\
    6 - (5 + 4) & = -(0 + 3 + 4) + (5 + 2 + 3) - (3 + 1 + 2) +  & \text{(Age 2+ at $t+1$)} \\
\end{align}

>>>>

Publishers of age-structured demographic data typically use some variant of the following scheme,
\begin{center}
\includegraphics[width=0.4\textwidth]{figures_accounts/fig_account_withage_nolex}
\end{center}
Population stocks stocks and flows are all disaggregated by the same age groups, which, in the case above, are ages 0, 1, and 2+. (The account in question might apply to non-human animals, or use a unit of measurement that is longer than a year.) The final age group includes everone over a certain age. Births are disaggregated by the age of the mother, rather than the age of the child being born, which is always 0.

@@

To do for each age group, need to deaths into ones that occurred to cohort already in age group and cohort entering age group:
\begin{center}
\includegraphics[width=0.5\textwidth]{figures_accounts/fig_account_withage_lex.pdf}
\end{center}

\begin{align}
    8 - (3 + 4) & = -2 + 3 - 1 & \text{(Age 0 at $t+1$)} \\   
    9 - 7 & = -(1 + 1) + (4 + 2) - (0 + 2) & \text{(Age 1 at $t+1$)} \\
    6 - (5 + 4) & = -(0 + 3 + 4) + (5 + 2 + 3) - (3 + 1 + 2)  & \text{(Age 2+ at $t+1$)} \\
\end{align}
